\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-02-15 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
making corrections

\medskip
The conservation of mass along with Darcy's law are the governing equations that describe the flow pattern. Finding an exact solution to some differential  equations is whether impossible or very time consuming. This is where people employ numerical analysis schemes to address the issue by creating a sequence  of approximations. This is done through discretization of the continuous differential equations. Therefore there are several methods that offer a means to obtain the approximate solutions, there appears that the most popular ones for the fluid flow equations are the Finite Difference Methods (FDM), the Finite DVolume Methods (FVM) and the Finite Element Methods. The latter is the one that will be used in this paper and more precisely a member of the FEM family, the COntrol-Volume-FEM method.

\KCnote{in our case only - In conventional reservoirs the principal forces that affect fluid flow include, viscous forces, effects of gravity and permeability diffrences while in unconventional gas reservoirs flow simulation models take into account the phenomena of adsorption and diffusion \citep{abdus_2015}. Even though the mechanisms of the instabilities may vary, however it is still a function of relative mobility, gravity, viscous forces and permeability differences. All these parameters are represented under one term in the global mass balance equation.}

@@

\medskip
The sections that follow include a summary of the main governing equations for multiphase compositional flow. The remainder of the paper will include a description of the viscous fingering along with the finite element method technique, a discussion of simulations results and the key conclusions. The analysis will consider ($1$)permeability heterogeities, ($2$)capturing the development of the interface and the evolution of fingers, ($3$)test-case comparison, but for now will neglect any gravitational effects.

>>>>

\medskip
The conservation of mass along with Darcy's law are the governing equations that describe the flow pattern. Finding an exact solution to some differential  equations is whether impossible or very time consuming. This is where people employ numerical analysis schemes to address the issue by creating a sequence  of approximations. This is done through discretization of the continuous differential equations. Therefore there are several methods that offer a means to obtain the approximate solutions, there appears that the most popular ones for the fluid flow equations are the Finite Difference Methods (FDM), the Finite DVolume Methods (FVM) and the Finite Element Methods. The latter is the one that will be used in this paper and more precisely a member of the FEM family, the Control-Volume FEM method (CVFEM).

%\KCnote{in our case only - In conventional reservoirs the principal forces that affect fluid flow include, viscous forces, effects of gravity and permeability diffrences while in unconventional gas reservoirs flow simulation models take into account the phenomena of adsorption and diffusion \citep{abdus_2015}. Even though the mechanisms of the instabilities may vary, however it is still a function of relative mobility, gravity, viscous forces and permeability differences. All these parameters are represented under one term in the global mass balance equation.}

@@

\medskip
\KCnote{ \blue{as soon as we finish the paper}, the sections that follow include a summary of the main governing equations for multiphase compositional flow. The remainder of the paper will include a description of the viscous fingering along with the finite element method technique, a discussion of simulations results and the key conclusions. The analysis will consider ($1$)permeability heterogeities, ($2$)capturing the development of the interface and the evolution of fingers, ($3$)test-case comparison, but for now will neglect any gravitational effects.}
